Quality Assessment of OpenStreetMap Footpath Data

### 2020-08-19 report/report.tex
Add note about where the road width measurements were obtained from

The standard road widths were obtained from a publication by the Swedish Transport Administration
\footnote{Vägars och gators utformning - Trafikverket. Publikation 2020:029. https://trafikverket.ineko.se/Files/sv-SE/71830/\\Ineko.Product.RelatedFiles/2020\_029\_vagar\_och\_gators\_utformning\_krav.pdf}
, and were presented as requirements on the minimum lane width for certain types of roads and applications.
These regulated minimum widths were used as a lower bound road with when examining the OSM dataset for potential overlap.
The upper bound was found by visual measurements of a few key locations in the Stockholm area using the Bing maps service.
Table \ref{table:road-widths} shows the minimum and maximum road widths that will be used in the overlap study.

\begin{table}[H]
    \begin{tabular}{lllll}
                      & Footpath & Residential & Secondary & Primary \\
        Minimum width & 2.0 m    & 6.0 m       & 6.5 m     & 8.0 m   \\
        Maximum width & 5.0 m    & 9.0 m       & 10.0 m    & 16.0 m
    \end{tabular}
    \captionof{table}{Standard road widths used for the overlap study}
    \label{table:road-widths}
\end{table}

>>>>

The standard road widths for the different types of car road were obtained from a publication by the Swedish Transport Administration
\footnote{Vägars och gators utformning - Trafikverket. Publikation 2020:029. https://trafikverket.ineko.se/Files/sv-SE/71830/\\Ineko.Product.RelatedFiles/2020\_029\_vagar\_och\_gators\_utformning\_krav.pdf}
, and were presented as requirements on the minimum lane width for certain types of roads and applications.
The minimum road widths were used as lower bounds when examining the OSM dataset for potential overlap.
The estimate standard width for footpaths was obtained from a set of manual sidewalk and walkway width measurements, obtained from visual inspection of publicly available satellite imagery from Bing Maps. A rounded value was chosen that was weighted towards the maximum results of those measurements.
Table \ref{table:road-widths} shows the road widths that were be used in the overlap study.

\begin{table}[H]
    \begin{tabular}{lllll}
                   & Footpath & Residential & Secondary & Primary \\
        Used width & 2.0 m    & 6.0 m       & 6.5 m     & 8.0 m   \\
    \end{tabular}
    \captionof{table}{Standard road widths used for the overlap study}
    \label{table:road-widths}
\end{table}
